Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-05 latex/robdml.tex
tex

\oo{[Deep metric learning problem setup]}

@@

\oo{[Quick review of existing defense methods]}

@@

>>>>

@@

Similar to what have been found for the classifiers, recent
works~\cite{robrank,advrank,advorder} also suggest that the embedding function
$\phi(\cdot)$ in DML is vulnerable to adversarial attacks.
%
Specifically, an imperceptible adversarial perturbation $r$ is added to the
input image $X$ ($\|r\|_p \leq \varepsilon$, $X+r\in \mathcal{X}$), so that its
embedding vector $\tilde{\vx}=\phi(X+r)$ will be moved off its original
location towards other positions to fulfill the attacker's goal.

Although attacks against DML has been widely studied~\cite{advrank,advorder},
the defense methods for improving adversarial robustness is much less explored.
%
As adversarial training~\cite{madry} remains to be one of the most effective
defense for classification, existing defense methods for DML are also adversarial
training-based.

\oo{[Quick review of existing defense methods]}
EST~\cite{advrank} and ACT~\cite{robrank}. Their issues.

@@

\subsection{\oo{Free Adversarial DML?}}

\subsection{\oo{Benchmark other DML loss?}}
